---
title: "Introduction to CoordGeom"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This starter package allows users to perform various geometric operations like calculate distance between two parallel lines, distance between two n dimensional vectors, intersection of lines in 3-Dimensional space and determine if two infinite lines are perpendicular in n-dimensional space. Our motivation in creating this package was to allow users with minimal experience in R programming to be able to perform these geometric calculations easily.

```{r setup}
library(CoordGeomR)
library(pracma)
```

### Determine whether two lines intersect with `is_intersection_3d()`

CoordGeomR makes it easy to determine whether two lines intersect in 3d space.

Note that if two parallel lines are provided, they will be considered as NOT intersecting. Also note that this function expects integer values for x, y, z coordinates. Values will be rounded if integer values are not provided.

This algorithm uses the following idea to test for intersection: Two (non parallel) lines intersect in 3d space if and only if they are coplanar.

Here is an example:

```{r intersection}
m1 <- c(1, 0, 0)
b1 <- c(0, 0, 0)
m2 <- c(0, 1, 0)
b2 <- c(0, 0, 0)

is_intersection_3d(m1, b1, m2, b2)
```

### Get distance between parallel lines with `dist_pll_lines_2d()`

Here is an example of how to calculate the distance between two parallel lines in 2-d space using CoordGeom.

```{r distance}

slope = 3
b1 = 4
b2 = 3
dist_pll_lines_2d(slope, b1, b2)

```

### Determine whether two lines are orthoganol with `is_orthogonal()`

Similarly, you can determine whether two lines are orthogonal (perpendicular) with `is_orthogonal()`.

```{r orthogonal}

m1 <- c(1, 0, 0)
m2 <- c(0, 1, 0)
is_orthogonal(m1, m2)

```

### Get distance between points with `get_distance()`

Finally, you can calculate distance between points in space with `get_distance()`.

We provide a few different options for how distance is calculated, with Euclidean being the default.

The full list of options are: "euclidean", "manhattan", "chebyshev", or "minkowski".

```{r}
x1 <- c(1, 2, 3, 4)
x2 <- c(5, 6, 7, 8)
get_distance(x1, x2, metric = "Euclidean")

get_distance(x1, x2, metric = "Manhattan")

get_distance(x1, x2, metric = "Chebyshev")

get_distance(x1, x2, metric = "Minkowski", 3)

```
